---
title: "Simple Power Analysis for RCS"
author: "Hayley Brooks"
date: "3/24/2022"
output: html_document
---

```{r setup, include=FALSE}
library("pwr")
```

Sample size will be 120 participants, 2 conditions of risky decision-making task, 4 orders:
1) control - strategy
2) control - control
3) strategy - strategy
4) strategy - control

Big question: is there a difference in temporal context effects between control and strategy conditions

What is our power for a t-test looking at whether the context effects at one timescale is different between control and strategy conditions on the first round of RDM task (60 in each condition)
```{r t-test}
pwr.t.test(d =.4,sig.level = .05, power = .8, type="two.sample"); # need 64 participants in each group to detect medium effect size with power of .8

pwr.t.test(n=60, d = .5, sig.level = .05, type="two.sample"); # power = 0.7752659
```

A lot of potential correlations but here are a few we may look at:
1. success and confidence in implementing strategy and p(gamble) following a large, positive outcome (e.g. >30)
2. success and confidence in implementing strategy and p(gamble) following a loss
3. success and confidence in implementing strategy and p(gamble) following a large shift ($20)
4. ERQ and WM
5. ERQ and success/confidence in strategy
6. WM and success/confidence in strategy

```{r correlations}
pwr.r.test(n=60, r=NULL, power = .8, sig.level=.05) # n=60
pwr.r.test(n=120, power=.8, sig.level=.05); # n=120

```

```{r glm}

pwr.f2.test(u = 3, f2 = .4, sig.level = 0.001, power = 0.8); # strategy*outcome (just first iteration of task)
# u = is number of regressors in model not including intercept
# f2 is effect size
```

